\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-07 Thesis.tex
primitives changed

To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks). For this we will be using the OMDoc (Open Mathematical Documents) format which, given an annotated set of documents, will provide us with the necessary HTML-representation of the information. This will also allow us to extract information about the semantic closeness of different pieces of information. Taking this as a starting point, we will visualize the dependencies of the information contained in these documents. We will visualize the dependencies in a simple but effective approach with basic elements of spatial narrative using the presentation framework Impress.js. The final product will allow for an interactive way of viewing a presentation.\\

@@

%Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}. The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\

%Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

%For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures. The frames can be mapped directly to the nodes/concepts that graphs use. Text and images are taken for granted within the frames. Similarly, the visual relation between different frames is very much like the relations between nodes. However, the relations can be much more expressive within Impress.js.\\

%Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information. Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for interactiveness.\\

%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft. Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\

@@

The development of presentation tools like Impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative. Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}. When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.\\

@@

\subsection{Impress.js}
\label{sec:Impressjs}

For the implementation of \sys, we chose to use Impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations. The open-source presentation framework \textbf{Impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's. It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers. The presentation data is entered in the html file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide. The \texttt{data-x} and \texttt{data-y} axis change the position of the element according to the normal x- and y-axes. The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
\definecolor{bg}{rgb}{0.90,0.90,0.90}

@@

Apart from these basic attributes, Impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}. As shown in \autoref{fig:Rotate} this allows the dependency graph to go into the third dimension.\\

@@

%Impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}. Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation. In this step we will define several models of how data is presented within a frame. Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}). Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within Impress.js.\\

@@

@@

In the last step, where the presentation is created, we use self-created boilerplate code, in which only some coordinates and the HTML for the slide is added. For the presentation Impress.JS was chosen such that the HTML code, automatically generated by lmh, can be reused. An important additional reason for the choice of Impress.JS is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and and \autoref{sec:Impressjs}.\\

Due to the choice of Impress.JS \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly. Impress.JS works in all modern browsers that support CSS 3D transforms.

@@

In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make important information bigger than less important information using the \texttt{data-scale} attribute. This would further add more semantic meaning to the slides. Additionally, one could think about adding a progress bar by using the work of Matthias Bilger \cite{bilger:npentrel15} to motivate users to continue.\\

>>>>

To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks). For this we will be using the OMDoc (Open Mathematical Documents) format which, given an annotated set of documents, will provide us with the necessary HTML-representation of the information. This will also allow us to extract information about the semantic closeness of different pieces of information. Taking this as a starting point, we will visualize the dependencies of the information contained in these documents. We will visualize the dependencies in a simple but effective approach with basic elements of spatial narrative using the presentation framework impress.js. The final product will allow for an interactive way of viewing a presentation.\\

@@

Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}. The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\

Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

For impress.js, the primitive elements are text, images, slides, and the visual relation between the different frame-like structures. The slides can be mapped directly to the nodes/concepts that graphs use. Text and images are taken for granted within the slides. Similarly, the visual relation between different slides is very much like the relations between nodes. However, the relations can be much more expressive within impress.js.\\

These relations or connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for additional interactiveness.\\

@@

The development of presentation tools like impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative. Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}. When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.\\

@@

\subsection{impress.js}
\label{sec:Impressjs}

For the implementation of \sys, we chose to use impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations. The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's. It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers. The presentation data is entered in the html file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide. The \texttt{data-x} and \texttt{data-y} axis change the position of the element according to the normal x- and y-axes. The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
\definecolor{bg}{rgb}{0.90,0.90,0.90}

@@

Apart from these basic attributes, impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}. As shown in \autoref{fig:Rotate} this allows the dependency graph to go into the third dimension.\\

@@

%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}. Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation. In this step we will define several models of how data is presented within a frame. Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}). Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within impress.js.\\

@@

% Layout
%The exact layout of the frames and the best visualization of the relations between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft. Ideally the added expressiveness that impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure, while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\

@@

In the last step, where the presentation is created, we use self-created boilerplate code, in which only some coordinates and the HTML for the slide is added. For the presentation impress.js was chosen such that the HTML code, automatically generated by lmh, can be reused. An important additional reason for the choice of impress.js is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and and \autoref{sec:Impressjs}.\\

Due to the choice of impress.js \cite{JSImpress:npentrel14}, older browsers and mobile browsers are not able to display the created presentations properly. mpress.js works in all modern browsers that support CSS 3D transforms.

@@

In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make use of relative size to additionally convey importance using impress.js' \texttt{data-scale} attribute. This would further add more semantic meaning to the slides. Additionally, one could think about adding a progress bar by using the work of Matthias Bilger \cite{bilger:npentrel15} to motivate users to continue.\\
